Multiset-trie data structure

### 2019-03-14 tex/tex/s_experiments.tex
updated experiment 5.

\subsection{Experiment 5} \label{s:exp5}
In this experiment, we demonstrate the performance of multiset-trie data structure compared to the inverted index based on the B+ tree. Both data structures are implemented in the programming language \CC, providing in this way an experimental setup for a fair comparison  [ref. to impl].

%% more details about implementation of the inverted files
((Presentation of the inverted index implementation? What about the smallest postings first?))

@@

((Is there anything special to be said about the artificially generated data?))

@@

We tested all three types of a query on all of the configurations from Table 1 which results in 18 experiments total, i.e., 6 experiments per query type. In each of the experiment, we measured an average time consumed by the data structure to process the query. The results of the exact search, sub-multiset and super-multiset search experiments are presented in tables Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and Table~\ref{t:res_sup}, respectively.

@@

We can see that multiset-trie outperforms inverted index in all of the experiments by up to 4 orders of magnitude. In an exact search, multiset-trie has to traverse only up to $\sigma+1$ nodes to get query result. It can be seen from results that with the increase of $\sigma$ the processing time for multiset-tire also increases. Multiplicity also affects the processing time; however, this happens passively. ((equivalent to $\sigma+1$?)) Multiplicity, or degree of a node $n$, defines the shape of multisets that are stored in multiset-trie. Thus, it affects the structure and density of the multiset-trie.

As for the inverted index, all three operations must first fetch all the postings for each particular element of a test multi-set. Afterward, the intersection of postings is computed to answer the query. The operations use more processing time than a simple tree traversal, which we can see from results. Postings are filtered on-the-fly to reduce the cost of the intersection. ((I do not get this: "Note that inverted index will also access at most $\sigma$ postings during search, but in addition to access some extra processing is required."))

@@

%% more details on this paragraph
((Can you characterize the sub-tree (num of nodes visited) visited by an operation more precisely? Can we say something about this? What is the size of the sub-tree visited by an operation? Why it is not very large? I did not try to finalize the following text.))
In the case of multiset-trie, only a traversal of the tree is required which is much faster than the processing of postings as we can see from results. In the worst case the whole tree is traversed, but so is for an inverted file. ((Can we see how...?))

>>>>

\subsection{Experiment 5} \label{s:exp5}
In this experiment, we demonstrate the performance of multiset-trie data structure compared to the inverted index based on the B+ tree. Both data structures are implemented in the programming language \CC, providing in this way an experimental setup for a fair comparison \cite{akulich2019mstrie}.

((Brief description of the implementation of the inverted files?))

@@

@@

We tested all three types of a query on all of the configurations from Table 1 which results in 18 experiments total, i.e., 6 experiments per query type. In each experiment, we measured an average time consumed by the data structure to process the query. The results of the exact search, sub-multiset and super-multiset search experiments are presented in tables Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and Table~\ref{t:res_sup}, respectively.

@@

We can see that multiset-trie outperforms inverted index in all of the experiments by up to 4 orders of magnitude. In an exact search, multiset-trie has to traverse only up to $\sigma+1$ nodes to get query result. It can be seen from results that with the increase of $\sigma$ the processing time for multiset-tire also increases. Multiplicity also affects the processing time; however, this happens passively. Multiplicity, or degree of a node $n$, defines the shape of multisets that are stored in multiset-trie. Thus, it affects the structure and density of the multiset-trie.

As for the inverted index, all three operations must first fetch all postings for each particular element of a test multi-set. Afterward, the intersection of postings is computed to answer the query. The operations use more processing time than a simple tree traversal, which we can see from results. Postings are filtered on-the-fly to reduce the cost of the intersection.

@@

In the case of multiset-trie, only a traversal of the tree is required which is much faster than the processing of postings as we can see from results. In the worst case the whole tree is traversed, but so is for an inverted file.
